---
title: "Modelling_CASA"
author: "Chaytanya Kumar"
date: "2022-12-02"
output: html_document
---

```{r}
library(readr)
library(car)
library(tidyverse)
Accident<-read_csv("/Users/chaytanya/Documents/Analytics /Accident_18_20.csv")
head(Accident)


Accident%>%
  mutate(Severity=if_else(Severity=='1',0,1))%>%
  mutate(D)->Accident
```


```{r}
model<-glm(Severity~Side+Weather_Condition+Sunrise_Sunset+Traffic_Signal+Crossing, family=binomial(link="logit"), data=Accident)
summary(model)
car::vif(model)

```


##Variable selection: 

`
```{r}
log.odds <- coef(model) # Extract the log-odds coefficients
odds <- exp(log.odds) # Convert the log-odds to odds print
print(cbind("Log-Odds" = log.odds,"Odds" = odds),digits = 2)
```

## Interpretation:
#The variables "Side", "Weather condition" (Cloudy), "DayParting"(Night) and "Traffic Signa"l(True) are highly significant as p-value < 0.05. 

While variables "Fog", "Snow" and "Crossing" are  significant as well(at alpha =0.10) 

On average, holding everything else constant, when the Side changes from Left to Right, the odds of High Severity increases  by a factor of 1.41(or increases by 41%).

On average, holding everything else constant, when the Weather changes from clear to Cloudy, the odds of High Severity increases  by 1.31(increase by a 31%).

On average, holding everything else constant, when the Day Parting changes from Day to Night, the odds of High Severity increases  by 1.62(increases by 62%).

On average,holding everything else constant, when the Traffic  Signal is present on the sight, the odds of High Severity decrease by  a factor of 0.56 (decreases by 44%).



